Designing and Developing a Personalised Recommender System

### 2021-02-10 paper/paper.tex
added processed data I use

\subsection{Input interface}
The input interface is the command line.
The program offers users opportunities to input information about themselves,
as well as make choices from a selection of items which the system provides or suggests.

>>>>

\subsection{Input interface}
The system has a command line based interface, so all user input of the input is given via the command line. 
The system recognises the active user by their unique user ID, some example IDs are provided in the README.txt 
file for testing and demonstration purposes. 
Only explicit user data is gathered in order to make the system more explainable and transparent.

The input interface is the command line.
The program offers users opportunities to input information about themselves,
as well as make choices from a selection of items which the system provides or suggests.
